\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\geometry{left=1in, right=1in, top=1in, bottom=1in}

\begin{document}

\begin{center}
    \textbf{\Huge Chanon Khanijoh} \\
    \vspace{0.2cm}
\end{center}

\noindent
\textbf{Contact Information:} \\
Address: Phet Kasem Soi 3, Wat Thapra, Bangkok Yai, Bangkok, Thailand 10600 \\
Phone: 0921190203 \\
Email: \href{mailto:Ckhanijoh@gmail.com}{Ckhanijoh@gmail.com} \\
LinkedIn: \href{https://www.linkedin.com/in/chanon-khanijoh-689991252}{Chanon Khanijoh} \\
GitHub: \href{https://github.com/KhChanon}{KhChanon} \\

\hrule
\vspace{0.3cm}

\noindent
\textbf{Profile:} \\
Dedicated computer engineer with hands-on experience in full-stack development and machine learning. Fast learner with a strong ability to collaborate with teams to deliver high-quality results.

\vspace{0.3cm}
\hrule
\vspace{0.3cm}

\noindent
\textbf{Education}
\begin{itemize}[leftmargin=0.5cm, noitemsep, topsep=0pt]
    \item International Pioneers School
    \item Saint Xavier's Senior Secondary School, India
    \item King Mongkut’s University of Technology Thonburi (KMUTT) \\ B.Eng in Computer
          Engineering \\ GPA: 3.45
\end{itemize}

\vspace{0.3cm}
\hrule
\vspace{0.3cm}

\noindent
\textbf{Professional Experience:}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{Internship at Pomelo} \\ \textit{Role:} Software Engineering Intern \\ \textit{Achievements:} Won first place for Pomelo Capstone Project

    \item \textbf{Internship at Plus Property} \\ \textit{Role:} Software Engineering Intern \\ \textit{Project:} Developed an object detection AI for license plate recognition

    \item \textbf{Playwork} \\
          \textit{Role:} Frontend Developer \\ 
          \textit{Project:} Worked on Mcneto CMS Project - \href{https://ccm-seller.mcneto.com/}{https://ccm-seller.mcneto.com} \\
          \textit{Tech Stack:} ReactJS, Redux, Sass, Bootstrap, Styled Component \\
          \textit{Highlights:}
          \begin{itemize}[leftmargin=0.5cm, noitemsep, topsep=0pt]
              \item Built reusable and customizable UI components that enable users to design their
                    own salepage templates.
              \item Modularized components for scalability and maintainability.
          \end{itemize}
    \item \textbf{Bangkok Bank} \\
          \textit{Role:} Frontend Developer \\ 
          \textit{Project:} Worked on oCRM Project \\
          \textit{Tech Stack:} ReactJS, ASP.NET \\
          \textit{Highlights:}
          \begin{itemize}[leftmargin=0.5cm, noitemsep, topsep=0pt]
              \item Build components and API to be integrated to Dynamics 365
          \end{itemize}
\end{itemize}

\hrule
\vspace{0.3cm}

\noindent
\textbf{Skills:}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{Languages:}
          \begin{itemize}[leftmargin=0.5cm, noitemsep, topsep=0pt]
              \item English (IELTS 7.0 - C1, TOEIC 935)
              \item Thai (Native)
          \end{itemize}
    \item \textbf{Programming Languages:}
          \begin{itemize}[leftmargin=0.5cm, noitemsep, topsep=0pt]
              \item Javascript, Typescript, CSS, HTML, Java, Python, C, R, SQL, C\#, LaTex
          \end{itemize}
    \item \textbf{Framework:}
          \begin{itemize}[leftmargin=0.5cm, noitemsep, topsep=0pt]
              \item NodeJS, ExpressJS, Flask (Python), Tailwind CSS, Styled Component,
                    Redux, ReactJS, Puppeteer, ASP.NET
          \end{itemize}
    \item \textbf{Database:}
          \begin{itemize}[leftmargin=0.5cm, noitemsep, topsep=0pt]
              \item MySQL, MongoDB
          \end{itemize}
    \item \textbf{AI \& Machine Learning:}
          \begin{itemize}[leftmargin=0.5cm, noitemsep, topsep=0pt]
              \item TensorFlow, PyTorch, OpenCV, Keras, YOLO
          \end{itemize}
    \item \textbf{Tools:}
          \begin{itemize}[leftmargin=0.5cm, noitemsep, topsep=0pt]
              \item Github, Bitbucket, Azure DevOps
              \item Postman, Docker
          \end{itemize}
\end{itemize}

\hrule
\vspace{0.3cm}

\noindent
\textbf{Projects:}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{HR Management System Website:} Worked as a full-stack developer using MySQL as the database.
    \item \textbf{Stock Simulation Website:} Worked as a full-stack developer using MongoDB as the database.
    \item \textbf{Dental AI Chatbot for Oral Question Answering and Post-Surgery Care:} Developed a QA Machine Learning Model for Question Answering Feature. Worked as a full-stack developer using MongoDB as the database.
    \item \textbf{Mcneto Salepage CMS:} Worked as a front-end developer using ReactJS, Redux, Sass, and Bootstrap.
    \item \textbf{oCRM for Bangkok Bank:} Worked as a Full-Stack developer using ReactJS and ASP.NET.
    \item \textbf{Real-Time group Chat Website:} Developed a real-time chat application using React for the frontend and Node.js / ASP.NET for the backend; implemented real-time messaging with SignalR.
\end{itemize}

\end{document}
